---
title: "Contributors"
author: 
  - name: Kevin Rue-Albrecht
    affiliation:
    - University of Oxford
    email: kevin.rue-albrecht@imm.ox.ac.uk
output: 
  BiocStyle::html_document:
    self_contained: yes
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: show
date: "`r doc_date()`"
package: "`r pkg_ver('BiocPkgToolsPlus')`"
vignette: >
  %\VignetteIndexEntry{Contributors}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}  
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    crop = NULL ## Related to https://stat.ethz.ch/pipermail/bioc-devel/2020-April/016656.html
)
```


```{r vignetteSetup, echo=FALSE, message=FALSE, warning = FALSE}
## Track time spent on making the vignette
startTime <- Sys.time()

## Bib setup
library("RefManageR")

## Write bibliography information
bib <- c(
    R = citation(),
    BiocStyle = citation("BiocStyle")[1],
    knitr = citation("knitr")[1],
    RefManageR = citation("RefManageR")[1],
    rmarkdown = citation("rmarkdown")[1],
    sessioninfo = citation("sessioninfo")[1],
    testthat = citation("testthat")[1],
    BiocPkgToolsPlus = citation("BiocPkgToolsPlus")[1]
)
```

# Libraries

Attach packages used in this vignettes.

```{r}
library("BiocPkgTools")
library("BiocPkgToolsPlus")
library("ggplot2")
```

# Best practices

Fetch the full Bioconductor package listing once for the whole notebook:

```{r biocpkglist}
biocpkglist <- get_all_biocpkglist(verbose = FALSE)
dim(biocpkglist)
```

# Use cases

## List of packages by contributor

The same person may be known by different name in different packages.
The function requires a named list:

- The name defines how they will be known in this analysis.
- The value is a character vector listing all their aliases to consider.

```{r}
author <- list(
  "Kevin Rue" = c(
    "Kevin Rue",
    "Kevin Rue-Albrecht"
  )
)
```

```{r}
out <- get_packages_by_author(author, pkg_list = biocpkglist)
out
```

One could then follow up by tracking how many of those packages the person has maintained over the years.

```{r}
out <- count_packages_over_time(out$Maintainer, pkg_list = biocpkglist)
out
```

```{r}
ggplot(out, aes(x = date, y = count)) +
  geom_point() +
  scale_y_continuous(breaks = function(x) {
    seq(ceiling(min(x)), floor(max(x)), by = 1)
  }) +
  theme_classic()
```


# Reproducibility

The `r Biocpkg("BiocPkgToolsPlus")` package `r Citep(bib[["BiocPkgToolsPlus"]])` was made possible thanks to:

* R `r Citep(bib[["R"]])`
* `r Biocpkg("BiocStyle")` `r Citep(bib[["BiocStyle"]])`
* `r CRANpkg("knitr")` `r Citep(bib[["knitr"]])`
* `r CRANpkg("RefManageR")` `r Citep(bib[["RefManageR"]])`
* `r CRANpkg("rmarkdown")` `r Citep(bib[["rmarkdown"]])`
* `r CRANpkg("sessioninfo")` `r Citep(bib[["sessioninfo"]])`
* `r CRANpkg("testthat")` `r Citep(bib[["testthat"]])`

This package was developed using `r BiocStyle::Biocpkg("biocthis")`.


Code for creating the vignette

```{r createVignette, eval=FALSE}
## Create the vignette
library("rmarkdown")
system.time(render("BiocPkgToolsPlus.Rmd", "BiocStyle::html_document"))

## Extract the R code
library("knitr")
knit("BiocPkgToolsPlus.Rmd", tangle = TRUE)
```

Date the vignette was generated.

```{r reproduce1, echo=FALSE}
## Date the vignette was generated
Sys.time()
```

Wallclock time spent generating the vignette.

```{r reproduce2, echo=FALSE}
## Processing time in seconds
totalTime <- diff(c(startTime, Sys.time()))
round(totalTime, digits = 3)
```

`R` session information.

```{r reproduce3, echo=FALSE}
## Session info
library("sessioninfo")
options(width = 120)
session_info()
```



# Bibliography

This vignette was generated using `r Biocpkg("BiocStyle")` `r Citep(bib[["BiocStyle"]])`
with `r CRANpkg("knitr")` `r Citep(bib[["knitr"]])` and `r CRANpkg("rmarkdown")` `r Citep(bib[["rmarkdown"]])` running behind the scenes.

Citations made with `r CRANpkg("RefManageR")` `r Citep(bib[["RefManageR"]])`.

```{r vignetteBiblio, results = "asis", echo = FALSE, warning = FALSE, message = FALSE}
## Print bibliography
PrintBibliography(bib, .opts = list(hyperlink = "to.doc", style = "html"))
```
