---
title: "Optimisations"
author: 
  - name: Kevin Rue-Albrecht
    affiliation:
    - University of Oxford
    email: kevin.rue-albrecht@imm.ox.ac.uk
output: 
  BiocStyle::html_document:
    self_contained: yes
    toc: true
    toc_float: true
    toc_depth: 2
    code_folding: show
date: "`r doc_date()`"
package: "`r pkg_ver('BiocPkgToolsPlus')`"
vignette: >
  %\VignetteIndexEntry{Optimisations}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}  
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    crop = NULL ## Related to https://stat.ethz.ch/pipermail/bioc-devel/2020-April/016656.html
)
```


```{r vignetteSetup, echo=FALSE, message=FALSE, warning = FALSE}
## Track time spent on making the vignette
startTime <- Sys.time()

## Bib setup
library("RefManageR")

## Write bibliography information
bib <- c(
    R = citation(),
    BiocStyle = citation("BiocStyle")[1],
    knitr = citation("knitr")[1],
    RefManageR = citation("RefManageR")[1],
    rmarkdown = citation("rmarkdown")[1],
    sessioninfo = citation("sessioninfo")[1],
    testthat = citation("testthat")[1],
    BiocPkgToolsPlus = citation("BiocPkgToolsPlus")[1]
)
```

# Libraries

Attach packages used in this vignettes.

```{r}
library("BiocPkgTools")
library("BiocPkgToolsPlus")
```

# Avoiding repeated calls to biocPkgList()

To save some typing, `get_packages_by_view()` calls `biocPkgList()` internally if `pkg_list` is `NULL` (the default).
This is convenient for one-off calls, but slow and verbose for multiple calls.

If you are calling `get_packages_by_view()` multiple times, it is more efficient to call `biocPkgList()` once and pass the result to `get_packages_by_view()`.

```{r}
pkg_list <- biocPkgList()
out1 <- get_packages_by_view("Spatial", pkg_list = pkg_list)
out2 <- get_packages_by_view("SingleCell", pkg_list = pkg_list)
```

# Wordclouds

The 'Getting started' vignette demonstrated a single method for producing a wordcloud.
This section offers alternatives.

Let's start by getting the count of co-occurrences for each biocViews term with a query term, obtained as follows:

```{r, message=FALSE}
library("dplyr")
out <- get_view_cooccurrences(view = "Spatial", pkg_list = pkg_list)
out |> arrange(desc(value))
```

In contrast to the interactive workclouds produced by `BiocStyle::CRANpkg("wordcloud2")`,
the `BiocStyle::CRANpkg("wordcloud")` package can be used to produce static wordclouds,
with a little bit more work:

```{r, message=FALSE, warning=FALSE, fig.cap="Wordcloud."}
library(wordcloud)
library(RColorBrewer)
set.seed(1)
wordcloud(
  words = out$package,
  freq = out$value,
  colors = brewer.pal(n = 8, name = "Dark2"),
  random.color = TRUE,
  rot.per=.2,
  scale=c(3, .5)
)
```

# Reproducibility

The `r Biocpkg("BiocPkgToolsPlus")` package `r Citep(bib[["BiocPkgToolsPlus"]])` was made possible thanks to:

* R `r Citep(bib[["R"]])`
* `r Biocpkg("BiocStyle")` `r Citep(bib[["BiocStyle"]])`
* `r CRANpkg("knitr")` `r Citep(bib[["knitr"]])`
* `r CRANpkg("RefManageR")` `r Citep(bib[["RefManageR"]])`
* `r CRANpkg("rmarkdown")` `r Citep(bib[["rmarkdown"]])`
* `r CRANpkg("sessioninfo")` `r Citep(bib[["sessioninfo"]])`
* `r CRANpkg("testthat")` `r Citep(bib[["testthat"]])`

This package was developed using `r BiocStyle::Biocpkg("biocthis")`.


Code for creating the vignette

```{r createVignette, eval=FALSE}
## Create the vignette
library("rmarkdown")
system.time(render("BiocPkgToolsPlus.Rmd", "BiocStyle::html_document"))

## Extract the R code
library("knitr")
knit("BiocPkgToolsPlus.Rmd", tangle = TRUE)
```

Date the vignette was generated.

```{r reproduce1, echo=FALSE}
## Date the vignette was generated
Sys.time()
```

Wallclock time spent generating the vignette.

```{r reproduce2, echo=FALSE}
## Processing time in seconds
totalTime <- diff(c(startTime, Sys.time()))
round(totalTime, digits = 3)
```

`R` session information.

```{r reproduce3, echo=FALSE}
## Session info
library("sessioninfo")
options(width = 120)
session_info()
```



# Bibliography

This vignette was generated using `r Biocpkg("BiocStyle")` `r Citep(bib[["BiocStyle"]])`
with `r CRANpkg("knitr")` `r Citep(bib[["knitr"]])` and `r CRANpkg("rmarkdown")` `r Citep(bib[["rmarkdown"]])` running behind the scenes.

Citations made with `r CRANpkg("RefManageR")` `r Citep(bib[["RefManageR"]])`.

```{r vignetteBiblio, results = "asis", echo = FALSE, warning = FALSE, message = FALSE}
## Print bibliography
PrintBibliography(bib, .opts = list(hyperlink = "to.doc", style = "html"))
```
